\sysfull

### 2017-08-07 paper/systemdescription.tex
added programming model overview

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\texttt{\_\_task\_\_ foo(){...}} & Task declaration\\
		\texttt{addTask()} & Build internal data structure for executor \\
		\texttt{run\_tasks()} & Task executor \\ %scheduler
		\texttt{next\_task()} & Transition to a new task\\
		%\texttt{PageFault()} & --- \\
		%\texttt{P()} & ---\\
		\hline
	\end{tabular}
\caption{Summary of \sys syntax: top---user-specific variables}
\label{tab:viper_syntax}
\end{table}

>>>>

\sys primarily consists of its compiler and the run time software support for
its execution model, but \sys also includes several lightweight programming
model extensions that are similar to those in prior work~\cite{chain,alpaca}.
Table~\ref{tab:viper_syntax} provides an overview of these extensions, which
can be used manually by a programmer, or can be added to a program
automatically, using \sys's compiler.  As in prior task-based intermittent
programming models, a \sys program is decomposed into tasks, which are
functions that are not allowed to have any direct callers.  The programmer
identifies a task by adding the {\tt task} keyword to the function's
declaration.  A programmer invokes one task, {\tt t} from another task {\tt u}
using {\tt next\_task( t )}, which atomically commits the state of {\tt u} and
transfers control to the entry point of {\tt t}.   A program has a single {\em
origin} task that executes first during the program's first execution; after a
power failure, in subsequent operating periods, \sys restarts from the task
that was executing just before the failure.

A \sys program manipulates {\em protected} state --- state that is accessed by
more than one task --- using the {\tt RP} and {\tt WP} operations, which read
and write (respectively) a protected variable. These operations convey to
\sys's runtime system which data must be protected through paging by the memory
manager.

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{task foo(){...}} & Task declaration\\
		\texttt{origin task foo(){...}} & Origin task declaration\\
		\texttt{next\_task()} & Transition to a new task\\
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\hline
	\end{tabular}
\caption{Summary of \sys's programming model extensions}
\label{tab:viper_syntax}
\end{table}
